\chapter{Conclusion}
\label{ch:concl}

TODO some nice quote

In this report, I have proposed a doctoral thesis on the topic
of factoid question answering.
So far, I have built a question answering system that exhibits
TODO performance and is still rapidly improving.  I have also
managed to reproduce state-of-art results in some of the sub-tasks
and identified and proposed a few original tasks tied to building
a state-of-art system in a real-world setting.

In my thesis, apart of describing my system building work, I would
like to focus on research connected to the Information Extraction
portion of the system.

As discussed above, vector embeddings are a booming area of semantic
NLP research with their ability to numerically capture meaning nuances,
and based on the presented survey of the field, I believe looking into
vector embedding approaches when manipulating natural text
(analyzing the question, understanding answer-bearing
passages and relation labels) is a perspective area of research.

Some scientific problems that I would like to tackle are connected
to the current limitations of vector embeddings themselves.
This includes building compound vector embeddings conveying
the meaning of a whole sentence rather than individual words,
and
exploring ways to embed or tie named entities, numerical quantities
and other arbitrary data to the conventional embeddings.

The scientific problems related to Information Extraction that
I plan to explore are in particular testing various relation
extraction strategies in the unstructured knowledge base context
and improving performance in this sub-task.
I expect to make the most progress by building embedded
representation of the manipulated data and leveraging it for
building appropriate classifiers.
It is unclear if that will eventually end up in the scope of my
thesis as well, but my sight is also set at using embeddings even
for tasks beyond basic factoid QA, like performing basic inference.

However, improving the system performance might lead to interesting
results in other parts of the system, involving Entity Linking,
Information Retrieval, Result Ranking etc.

\section{Acknowledgements}

I would like to thank my main supervisor Dr. Petr Pošík
for his guidance, support, but also giving me the freedom to
eventually take a different direction of scientific pursuit.
I would also like to thank my specialist supervisor Dr. Jan Šedivý
for supporting me in this new topic of research, his result-focused
guidance and giving me great opportunities to boost the development
of my system.
